\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2010-08-14 article.tex
Added pattern movements to the classification section

  Each pattern movement is tagged on the basis of their English description
  from the condensed encyclopedia. In addition, suitable tags is attached to
  the dataset while performing the pattern to add necessary detail.

@@

  Information about the stance type is presented first, followed by stance
  side (left, right or none where applicable --- ie. sitting stance, technique
  height (low, middle, high), technique side (left arm or right arm, can also
  be both), direction of the technique (when needed), primary technique type
  (attack, block, kick), technique group (punch, strike, thrust), tool group
  (forearm, knife hand, finger etc.), tool (inner forearm, outer forearm,
  double finger etc.), and finally motion type (normal motion, slow motion,
  consecutive motion and so on).

@@

% TODO: vurderinger på teknikker, se notater i wikien

\begin{itemize}
  \item
    \emph{Yul-Gok Tul}
    \begin{itemize}
      \item
        {\bf Movement 24}, \emph{Gunnun so ap palkup bandae taerigi}, is
        tagged with $\{front\_strike\}$ due to the English description of
        striking with the right front elbow.
      \item
        {\bf Movement 27}, \emph{Gunnun so ap palkup bandae taerigi}, is
        tagged with $\{front\_strike\}$ due to the English description of
        striking with the left front elbow.
    \end{itemize}
  \item
    \emph{Joong-Gun Tul}
    \begin{itemize}
      \item
        {\bf Movement 8}, \emph{Gunnun so wipalkup taerigi}, is tagged
        $\{upper\_strike, \: upper\_elbow\}$ since the English description
        says that the movement is ``a right upper elbow strike.''
      \item
        {\bf Movement 10}, \emph{Gunnun so wipalkup taerigi}, is tagged
        $\{upper\_strike, \: upper\_elbow\}$ since the English description
        says that the movement is ``a left upper elbow strike.''
      \item
        {\bf Movement 11}, \emph{Gunnun so sang sewo jirugi}, is tagged as a
        left and right technique, with $\{left\_technique, \:
        right\_technique\}$.
      \item
        {\bf Movement 12}, \emph{Gunnun so sang dwijibo jirugi}, is tagged as
        a left and right technique, with $\{left\_technique, \:
        right\_technique\}$.
      \item
        {\bf Movement 27}, \emph{Nachuo so sonbadak noollo makgi}, is tagged
        as a $\{middle\_technique, \: low\_technique\}$ because the left hand
        is in the middle section and the right hand, forming the pressing
        block, is in the low section of the body. Furthermore, the movement
        has been tagged as a $\{right\_technique, \: left\_technique\}$ to
        reflect that both hands are being used.
      \item
        {\bf Movement 29}, \emph{Nachuo so sonbadak noollo makgi}, is tagged
        as a $\{middle\_technique, \: low\_technique\}$ because the right hand
        is in the middle section and the left hand, forming the pressing
        block, is in the low section of the body. Furthermore, the movement
        has been tagged as a $\{right\_technique, \: left\_technique\}$ to
        reflect that both hands are being used.
    \end{itemize}
  \item
    \emph{Choong-Moo Tul}
    \begin{itemize}
      \item
        {\bf Movement 19
    \end{itemize}
  \item
    \emph{Pragmatic}
    \begin{itemize}
      \item
        Free software is available for experimentation and testing.
      \item
        Most readers of this text have a background in relational technology. 
    \end{itemize}
\end{itemize}

\Section{Results}

@@

\Section{Conclusions}

@@

% Unnumbered section (note the '*')
\section*{Acknowledgments}

  % Thanks to Master Nicolaisen (VII. Dan) for pointing out that I already had
  % found a problem statement when I was still looking for one
  %
  % Odd-Magne Hansen (III. Dan) for helping me with the terminology, and
  % general feedback
  Todo.

>>>>

  Each pattern movement is tagged on the basis of their English description
  from the condensed encyclopedia. In addition, suitable tags were attached to
  the dataset while performing the pattern to add necessary detail.

@@

  Information about the stance type is presented first, followed by stance
  side (left, right or none where applicable --- ie. sitting stance),
  technique height (low, middle, high), technique side (left arm or right arm,
  can also be both), direction of the technique (when needed), primary
  technique type (attack, block, kick), technique group (punch, strike,
  thrust), tool group (forearm, knife hand, finger etc.), tool (inner forearm,
  outer forearm, double finger etc.), and finally motion type (normal motion,
  slow motion, consecutive motion and so on).

@@

% TODO: introduction

\begin{itemize}
  \item
    \emph{Yul-Gok Tul}
    \begin{itemize}
      \item
        {\bf Movement 24}, \emph{Gunnun so ap palkup bandae taerigi}, is
        tagged with $\{front\_strike\}$ due to the English description of
        striking with the right front elbow.
      \item
        {\bf Movement 27}, \emph{Gunnun so ap palkup bandae taerigi}, is
        tagged with $\{front\_strike\}$ due to the English description of
        striking with the left front elbow.
    \end{itemize}
  \item
    \emph{Joong-Gun Tul}
    \begin{itemize}
      \item
        {\bf Movement 8}, \emph{Gunnun so wipalkup taerigi}, is tagged
        $\{upper\_strike, \: upper\_elbow\}$ since the English description
        says that the movement is ``a right upper elbow strike.''
      \item
        {\bf Movement 10}, \emph{Gunnun so wipalkup taerigi}, is tagged
        $\{upper\_strike, \: upper\_elbow\}$ since the English description
        says that the movement is ``a left upper elbow strike.''
      \item
        {\bf Movement 11}, \emph{Gunnun so sang sewo jirugi}, is tagged as a
        left and right technique, with $\{left\_technique, \:
        right\_technique\}$.
      \item
        {\bf Movement 12}, \emph{Gunnun so sang dwijibo jirugi}, is tagged as
        a left and right technique, with $\{left\_technique, \:
        right\_technique\}$.
      \item
        {\bf Movement 27}, \emph{Nachuo so sonbadak noollo makgi}, is tagged
        as a $\{middle\_technique, \: low\_technique\}$ because the left hand
        is in the middle section and the right hand, forming the pressing
        block, is in the low section of the body. Furthermore, the movement
        has been tagged as a $\{right\_technique, \: left\_technique\}$ to
        reflect that both hands are being used.
      \item
        {\bf Movement 29}, \emph{Nachuo so sonbadak noollo makgi}, is tagged
        as a $\{middle\_technique, \: low\_technique\}$ because the right hand
        is in the middle section and the left hand, forming the pressing
        block, is in the low section of the body. Furthermore, the movement
        has been tagged as a $\{right\_technique, \: left\_technique\}$ to
        reflect that both hands are being used.
    \end{itemize}
  \item
    \emph{Po-Eun Tul}
    \begin{itemize}
      \item
        {\bf Movement 6}, \emph{Annun so ap joomuk noollo makgi}, consist of
        two blocks. The first is a ``pressing block with the left fore fist,''
        and the second one is a ``side front block with the right inner
        forearm.'' When searching, this movement will only register as one
        block.
      \item
        {\bf Movement 7}, \emph{Annun so ap joomuk noollo makgi}, consist of
        two blocks. The first is a ``pressing block with the right fore
        fist,'' and the second one is a ``side front block with the left inner
        forearm.'' When searching, this movement will only register as one
        block.
      \item
        {\bf Movement 24}, \emph{Annun so ap joomuk noollo makgi}, consist of
        two blocks. The first is a ``pressing block with the right fore
        fist,'' and the second one is a ``side front block with the left inner
        forearm.'' When searching, this movement will only register as one
        block.
      \item
        {\bf Movement 25}, \emph{Annun so ap joomuk noollo makgi}, consist of
        two blocks. The first is a ``pressing block with the left fore fist,''
        and the second one is a ``side front block with the right inner
        forearm.'' When searching, this movement will only register as one
        block.
    \end{itemize}

    Movements 6, 7, 24 and 25 for pattern Po-Eun has the following tags
    attached:

  \begin{align*}
    \{sitting\_stance, \: low\_technique, \: high\_technique, \\
    left\_technique, \: right\_technique, \: block, \\
    pressing\_block, fore\_fist, \: forearm, \: inner\_forearm, \\
    side\_front\_block, \: continuous\_motion\}
  \end{align*}

  \item
    \emph{Ge-Baek Tul}
    \begin{itemize}
      \item
        The height of the kick in {\bf movement 23}, \emph{Twimyo yopcha
        jirugi}, is not registered.
    \end{itemize}
  \item
    \emph{Choong-Jang Tul}
    \begin{itemize}
      \item
        {\bf Movement 19}, \emph{Moorup najunde apcha busigi}, is tagged with
        $\{front\_snap\_kick, \: knee\}$ which has an effect on the total of
        low front snap kicks.
      \item
        {\bf Movement 41}, \emph{Gunnun so sang sonkal soopyong taerigi}, is
        tagged with $\{knife\_hand, \: twin\_knife\_hand\}$.
    \end{itemize}
\end{itemize}

%\Section{Results}

@@

%\Section{Conclusions}

@@

% Unnumbered section (note the '*')
%\section*{Acknowledgments}

  % Thanks to Master Nicolaisen (VII. Dan) for pointing out that I already had
  % found a problem statement when I was still looking for one
  %
  % Odd-Magne Hansen (III. Dan) for helping me with the terminology, and
  % general feedback
  %Todo.
